Workflow for Ecov Recruitment Analysis

### 2024-01-23 Ecov_study/recruitment_functions/Workflow_Ecov_Recruitment_Project.Rmd
mohn's rho analysis
script and plots

5. Cleaning up script **compare_projections.R**
   + this calculates mohn's rho for user-specified number of peels, evaluates relative error from peel 10 to peel 0, ...
   + Runtime ...
   + **<span style="color: blue;">STATUS: pending... beta unstandardized; </span>**

@@

# Figures

>>>>

6. Look at retrospective bias **mohns_rho_analysis.R**
   + this calculates mohn's rho for user-specified number of peels
   + regression tree and plots for SSB, Fbar, Recruitment and also for recruitment random effects
   + Runtime 2 * 1.6 hours
   + **<span style="color: blue;">STATUS: done beta unstandardized; </span>**

7. Cleaning up script **compare_projections.R**
   + evaluates relative error in projections between peel 10 and truth ...
   + Runtime ...
   + **<span style="color: blue;">STATUS: pending... beta unstandardized; </span>**

@@

# Figures and Tables

+ SSRTWG/Ecov_study/recruitment_functions/plots_beta_fix
+ SSRTWG/Ecov_study/recruitment_functions/tables
